What We Eval in the Shadows

### 2021-09-08 paper/main.tex
Even better layout

\begin{wrapfigure}{r}{7cm}
	\includegraphics[width=7cm]{pkgs-eval-callsites-hist.pdf}
	\caption{ \eval call sites}\label{fig:pkgs-eval-callsites-hist}
\end{wrapfigure}

@@

\begin{wraptable}{r}{5cm} \vspace*{-2mm}\ \small  \centering
  \begin{tabular}{r@{\,}r@{\,}l@{\,}r|r@{\,}r@{\,}l@{}r} \toprule
    \multicolumn{3}{c}{\bf \#calls} & \bf \#sites &
     \multicolumn{3}{c}{\bf \#calls} & \bf \#sites \\\midrule
    \tt 0 &--& \tt 50    & \packageRunbina & \tt 501 &--& \tt 1000   & \packageRunbine\\
    \tt 51 &--& \tt 100  & \packageRunbinb & \tt 1001 &--& \tt 1500  & \packageRunbinf\\
    \tt 101 &--& \tt 250 & \packageRunbinc & \tt 1501 &--& \tt 2000  & \packageRunbing\\
    \tt 251 &--& \tt 500 & \packageRunbind & \tt 2001 &--& \tt 3000 & \packageRunbinh\\\bottomrule
  \end{tabular}
  \caption{Normalized calls} \label{tab:cn}
\end{wraptable}

@@

\begin{wrapfigure}{r}{6.2cm}
\hspace{-25mm} \includegraphics[width=0.8\textwidth]{package_size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{r}{7cm}
	\hspace*{-1cm}\includegraphics[width=9cm]{pkgs-eval-callsites-hist.pdf}
	\caption{ \eval call sites}\label{fig:pkgs-eval-callsites-hist}
\end{wrapfigure}

@@

\begin{wraptable}{r}{5cm}  \small  \centering
  \begin{tabular}{r@{\,}r@{\,}l@{\,}r|r@{\,}r@{\,}l@{}r} \toprule
    \multicolumn{3}{c}{\bf \#calls} & \bf \#sites &
     \multicolumn{3}{c}{\bf \#calls} & \bf \#sites \\\midrule
    \tt 0 &--& \tt 50    & \packageRunbina & \tt 501 &--& \tt 1000   & \packageRunbine\\
    \tt 51 &--& \tt 100  & \packageRunbinb & \tt 1001 &--& \tt 1500  & \packageRunbinf\\
    \tt 101 &--& \tt 250 & \packageRunbinc & \tt 1501 &--& \tt 2000  & \packageRunbing\\
    \tt 251 &--& \tt 500 & \packageRunbind & \tt 2001 &--& \tt 3000 & \packageRunbinh\\\bottomrule
  \end{tabular}
  \caption{Normalized calls} \label{tab:cn}
  \vspace{-0.5cm}
\end{wraptable}

@@

\begin{wrapfigure}{r}{6.2cm}
\hspace{-3.3cm} \includegraphics[width=0.9\textwidth]{package_size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}
